---
title: "ArabBarometR Graphing Guide"
author: "MaryClare Roche"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

# Introduction {#introduction .unnumbered}

Placeholder


## Purpose {.unnumbered}
## Best Practices {.unnumbered}
## General Guide Process {.unnumbered}
## Example Data {.unnumbered}
## Header Code {#headercode .unnumbered}

<!--chapter:end:index.rmd-->


# Package Workflow and Grammar {- #package-workflow}

Placeholder


## `calculate_` functions {-}
## `plot_` functions {-}
## `AB_save()` {-}

<!--chapter:end:Workflow_and_Grammar.Rmd-->

# <span style = "font-family: Tajawal;"> العربيه </span>{- #arabic}

This guide is written in English for several reasons. Primarily, MaryClare does not speak Arabic. Secondarily, computers generally and programming languages specifically do not mix well with Arabic. It is best to start learning with the simplest case, and English is the simplest case when it comes to programming.

However just because programming with Arabic is difficult, that does not mean it cannot be done. The functions in the package are designed to work with Arabic data just as they do with English data. Using the Arabic Arab Barometer data set should produce the same outcome as the English Arab Barometer data set, only with Arabic adjustments. For example, using data data to create plots will produce plots with Arabic text.

If everything works perfectly, the package should be able to detect when Arabic or English is being used an adjust accordingly. If the package makes a mistake, you can force it to a specific language by supplying either `"ar"` or `"en"` to the parameter `.language` in the function you are using.

<!--chapter:end:Arabic.Rmd-->


# Table of Contents {-}

Placeholder



<!--chapter:end:00-ToC.Rmd-->


# (PART) Data Prepperation Functions {- #prepare-data}

Placeholder


## TL;DR
#### Example:
## `recode_country()`
### Example:
## Demographic functions
### Basics
#### Example:
## Advanced
## `age_demographic()`
## `education_demographic()`
### Examples:
## `dummy_all()` {#dummy-all}
### Examples:
## `dummy_select()`
### Examples:
## In Practice
### Example:

<!--chapter:end:001-Package-Intro.Rmd-->


# (PART) Cross Tabulation Graphs {-}
# Single Country Overall Graphs {#chapter-1}

Placeholder


## Create a Single Graph {#chapter-1-1}
### TL;DR {- #tldr-chapter1-single}
### Create a Summary {#chapter-1-1-1}
### Plot the Summary {#chapter-1-1-2}
## Create Many Graphs {#chapter-1-2}
### TL;DR {#tldr-chapter1-many -}
### Identify the Variables {#chapter-1-2-1}
### Create Summaries {#chapter-1-2-2}
### Plot the Summaries {#plot-many-graphs-single-country}

<!--chapter:end:01-SingleCountryOverall.Rmd-->


# Single Country Demographic Plots {#chapter-2}

Placeholder


## Create a Single Graph
### TL;DR {#tldr-chapter2-single -}
### Creating a Summary
### Plotting the Summary
## Create Many Graphs
### TL;DR {#tldr-chapter2-mnay -}
### Create Summaries
### Plot the Summaries {#plot-many-graphs-single-country-demographic}
## Extras
### Font Size
### Colors
### Warnings

<!--chapter:end:02-SingleCountryDemographic.Rmd-->


# Comparative Overall Graphs {#chapter-3}

Placeholder


## Create a Single Graph
### TL;DR {#tildr-chapter3-single -}
### Create a Summary
### Plot the Summary
## Create Many Graphs
### TL;DR {#tildr-chapter3-mnay -}
### Identify the Variables
### Create Summaries
### Plot the Summaries {#plot-many-comparative}

<!--chapter:end:03-ComparativeOverall.Rmd-->


# Comparative Demographic Graphs {#chapter-4}

Placeholder


## Create a Single Graph
### TL;DR {#tldr-chapter4-single -}
### Creating a Summary
### Plotting the Summary
## Create Many Graphs
### TL;DR {#tldr-chapter4-many -}
### Create Summaries
### Plot the Summaries {#plot-many-comparative-demographic}

<!--chapter:end:04-ComparativeDemographic.Rmd-->


# (PART) Stacked Plots {-}
# Stacked Plots

Placeholder


## Create a Single Graph
### Create a Summary
### Plot the Summary
## Create Many Graphs
### Identify the Variables
### Create Many Summaries
### Create Many Plots
## Extras
### Long Legends
### Font Size
### Colors
### Order

<!--chapter:end:13-Stacked.Rmd-->


# (PART) Multiquestion Graphs {-}
# Single Country Multi-Question Plots {#new-chapter-9}

Placeholder


### TL;DR {-}
#### "Short" Summary {- #tldr-short-smry-multiq}
#### "Long" Summary {- #tldr-long-smry-multiq}
## Prep Work {#new-chapter-9-1}
### Question Vector {#new-chapter-9-1-1}
### Question Labels {#new-chapter-9-1-2}
## Create a Multiquestion Summary
### "Short" Summary {#short-summary-calc}
### "Long" Summary {#long-summary-calc}
## Plot the Summary {#new-chapter-9-2}
### "Short" Plots
### "Long" Plots
## Extras {#new-chapter-9-3}
### Explict Grid Example {#new-chapter-9-3-3}
#### "Short" Summary {-}
#### "Long" Summary {-}
### Setting Colors {#new-chapter-9-3-1}
### Warnings {#new-chapter-9-warnings}

<!--chapter:end:Individual_Multiquestion_Short.Rmd-->


# Demographic Single Country Multi-Question Plots {#chapter-dem-multiq}

Placeholder


### TL;DR {-}
## Prep Work
### Question Vector {#chapter-dem-multiq-1-1}
### Question Labels {#chapter-dem-multiq-1-2}
## Create a Summary
## Plot a Multiquestion Demographic Summary for an Individual Country
## Extras
### Setting Colors {#chapter-dem-multiq-3-1}
### Warnings {#chapter-dem-multiq-warnings}

<!--chapter:end:ind-dem-multiq.Rmd-->


# Comparative Multi-Question Plots {#chapter-10}

Placeholder


### TL;DR {-}
## Prep Work {#chapter-10-1}
### Question List {#chapter-10-1-1}
### Question Labels {#chapter-10-1-2}
## Create a Summary {#chapter-10-2}
## Plot a Comparative Multiquestion Graph {#chapter-10-3}
## Extras {#chapter-10-4}
### Setting Colors {#chapter-10-4-1}
### Select Countries {#chapter-10-4-2}
### Explict Grid Example {#chapter-10-4-3}
### Warnings {#chapter-10-warnings}

<!--chapter:end:10-ComparativeMutliQuestion.Rmd-->


# Single Country Trend Graphs {#chapter-5}

Placeholder


## TL;DR {-}
## Prep Work {#chapter-5-1-1}
### Create a Data Frame List {- #chp5-trend-df-list}
### Create a Date Vector {- #chp5-trend-date-vector}
## Create a Summary  {#chapter-5-1-2}
## Plot the Summary {#chapter-5-1-3}
## Extras 
### Font Size
### Colors

<!--chapter:end:05-SingleTrend.Rmd-->


# Single Country Demographic Trend Graphs {#chapter-6}

Placeholder


## TL;DR {-}
## Prep Work {#chapter-6-1-1}
### Create a Data Frame List {- #chp6-trend-df-list}
### Create a Date Vector {- #chp6-trend-date-vector}
## Create a Summary {#chapter-6-1-2}
## Plot the Summary {#chapter-6-1-3}
## Extras 
### Human Readable
### Font Size
### Colors

<!--chapter:end:06-SingleDemographicTrend.Rmd-->


# Comparative Country Trend Graphs {#chapter-7}

Placeholder


## TL;DR {-}
## Prep Work {#chapter-7-1-1}
### Create a Data Frame List {#chp7-trend-df-list}
### Create a Date Vector {#chp7-trend-date-vector}
## Create a Summary {#chapter-7-2-1}
## Plot the Summary {#chapter-7-3-1}
## Extras
### Human Readable
### Country Wrap
### Select Countries
### Font Size
### Colors

<!--chapter:end:07-ComparativeTrend.Rmd-->


# Comparative Country Demographic Trend Graphs {#chapter-8}

Placeholder


## TL;DR {-}
## Prep Work {#chapter-8-1-1}
### Create a Data Frame List {- #chp8-trend-df-list}
### Create a Date Vector {- #chp8-trend-date-vector}
## Create a Summary {#chapter-8-2}
## Plot the Summary {#chapter-8-3}
### Option 1: Facet choice is `"Country"` (default)
### Option 2: Facet choice is `"demographic"` {-}
## Extras
### Human Readable
### Select Countries
### Font Size
### Colors

<!--chapter:end:08-ComparativeDemographicTrend.Rmd-->


# Single Country Multi-Question Trend Plots {#chapter-12}

Placeholder


## TL;DR {-}
## Prep Work {#chapter-12-1}
### Question Vector {#chapter-12-1-1}
### Question Labels {#chapter-12-1-2}
### Create a Data Frame List {#chapter-12-1-3}
### Create a Date Vector {#chapter-12-1-4}
## Create a Summary {#chapter-12-2-1}
## Plot the Summary {#chapter-12-3-1}
## Extras 
### Human Readable
### Legend Names
### Font Size
### Colors

<!--chapter:end:12-SingleCountryMultiQuestionTrend.Rmd-->


# (PART) All Things Colors {-}
# Color Options

Placeholder


## Available Colors
## Available Palettes

<!--chapter:end:9801-ColorPart.Rmd-->

# Change Default Colors {#change-colors}


## Basic Cross Tabs {#change-colors-basic}

The parameter is called **`.color_choice`**. This parameter accepts either a color name from `ArabBarometR` or a hex code.

```{r How.3.1-Complete-Code-Example, fig.dim=c(13,12)}

survey1  |> 
  calculate_ind_smry("Q1COVID19",
                            "Algeria") |>
  plot_ind_smry(.color_choice = "zeke")

survey1 |>
  calculate_comp_smry("Q1COVID19") |>
  plot_comp_smry(.color_choice = "#FF5E64")


```


## Demographic Cross Tabs {#change-colors-demographic}

The parameter to change is called **`.color_choice`**. This parameter accepts any of the following:

  * `"default"` (which it is set to),
  * the name of an `ArabBarometR` color palette,
  * a vector of `ArabBarometR` color names, or
  * a vector of hex codes.
  
If you choose to use a vector of either color names or hex codes, it **must** be the same length as the number of demographic categories. For example, the `gender` demographic has two categories, so a vector of custom colors needs to be length two. You can check the number of categories by looking at the data frame you are plotting.

```{r How.3.2-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE}

survey1 |>
  calculate_ind_smry_dem("Q1COVID19",
                                        "Algeria",
                                        demographic = "gender") |> 
  plot_ind_smry_dem(.color_choice = "blue pair")

survey1 |>
  calculate_comp_smry_dem("Q1COVID19",
                                  demographic = "gender") |> 
  plot_comp_smry_dem(.color_choice = c("salma","mary clare"))

data_frame_2_plot <- survey1 |>
  calculate_comp_smry_dem("Q1COVID19",
                                  demographic = "Q101") 

data_frame_2_plot


# 6 categories means 6 colors needed
data_frame_2_plot |> 
  plot_comp_smry_dem(.color_choice = c("#0098BE",
                                                         "#DF6E21",
                                                         "#AC517F",
                                                         "#7CBBC7",
                                                         "#796391",
                                                         "#CF83A3"))


```


## Stacked Graphs {#change-colors-stacked}

The parameter is called **`.color_choice`**. The parameter accepts any of the following:

  * the name of an `ArabBarometR` color palette,
  * a vector of `ArabBarometR` color names, or
  * a vector of hex codes.
  
If you choose to use a vector of either color names or hex codes, it **must** be the same length as the number of categories. Recall that the categories "don't know" and "refuse" are combined into a single category unless otherwise specified. When determining the number of colors you need for your vector, only count the "don't know" and "refuse" categories as one category.

Take `Q2061A` as an example. In the first survey of wave six, question `Q2061A` had ten response options including "don't know" and "refuse". The `calculate_comp_smry_stacked()` function combines "don't konw" and "refuse" into one category, so the color palette vector only needs to be length nine.

```{r How.3.3-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE}

calculate_comp_smry_stacked(survey1,
                     "Q2061A") |>
  plot_comp_smry_stacked(.caption = "Arab Barometer Wave VI, Survey 1",
                    .color_choice = "soft rainbow")

calculate_comp_smry_stacked(survey1,
                     "Q2061A") |>
  plot_comp_smry_stacked(.caption = "Arab Barometer Wave VI, Survey 1",
                    .color_choice = c("AB blue",
                                       "AB orange",
                                       "AB magenta",
                                       "AB light blue",
                                       "AB purple",
                                       "AB pink",
                                       "AB yellow",
                                       "zeke",
                                       "pale green"))


```

## Trend Graphs {#change-colors-trend}

By default trend graphs are created in the brand color assigned to them. If you wish to change the color, you can do so by setting the parameter `.color_choice` to either a hex code or a color from `ArabBarometer_colors()`.

### Single Country Trend Graphs {- #change-colors-trend-single}

Changing the color for single country trend graphs is exactly the same as for [basic cross tabs](#change-colors-basic), only using a different parameter name.

```{r How.3.4-Complete-Code-Example, fig.dim=c(13,12),eval=FALSE}

calculate_ind_trend("Q1COVID19",
                    df_list,
                    survey_dates,
                    "Algeria") |> 
  plot_ind_trend(.caption = "Arab Barometer Wave VI, Algeria",
                      .color_choice = "bright apple")  # Arab Barometer color name


calculate_ind_trend("Q1COVID19",
                    df_list,
                    survey_dates,
                    "Algeria") |> 
  plot_ind_trend(.caption = "Arab Barometer Wave VI, Algeria",
                      .color_choice = "#C8C6A2")  # Arab Barometer color name

```

### Comparative Trend Graphs {- #change-colors-trend-comparative}

There is greater flexibility in colors for comparative trend graphs. The user may supply a named or unnamed vector of hex codes or Arab Barometer brand colors. 


```{r How.3.5-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE,eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Survey 2",
                  "Survey 3")

# Unnamed color example
calculate_comp_trend("Q1COVID19",
                df_list,
                ab_survey_dates) |> 
  plot_comp_trend(.caption = "Arab Barometer Wave VI",
                select_countries = c("Lebanon","Morocco"),
                .color_choice = c("bright apple","james bond"))


# Named color example
trend_colors <- c("bright apple","james bond")
names(trend_colors) <- c("Morocco","Lebanon")

calculate_comp_trend("Q1COVID19",
                df_list,
                ab_survey_dates) |> 
  plot_comp_trend(.caption = "Arab Barometer Wave VI",
                select_countries = c("Lebanon","Morocco"),
                .color_choice = trend_colors)

```

The user can also change the color of some but not all countries.

```{r How.3.6-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE,eval=FALSE}
# Change one color example
calculate_comp_trend("Q1COVID19",
                df_list,
                ab_survey_dates) |> 
  plot_comp_trend(.caption = "Arab Barometer Wave VI",
                select_countries = c("Lebanon","Morocco"),
                .color_choice = c("Lebanon" = "#C8C6A2"))


```

<!--chapter:end:9803-ColorChange.Rmd-->


# Highlight Certain Countries

Placeholder


## Single Country Highlight
## Multiple Country Highlight
## Change Highlight Color

<!--chapter:end:9804-HighlightCountry.Rmd-->

# (PART) How do I ...? {-}
# Change the Font Size {#change-font-size}


```{r How.Change-Font-Size-Complete-Code-Example, fig.dim=c(13,12)}

survey1 |>
  calculate_ind_smry("Q1COVID19",
                     select_country = "Algeria") |>
  plot_ind_smry(.caption = "Arab Barometer Wave VI, Survey I, Algeria",
                       theme.title_size = 28,        # Changes title size
                       theme.subtitle_size = 14,     # Changes subtitle size
                       theme.caption_size = 20,      # Changes caption size
                       theme.axis_x_text_size = 26,  # Changes x-axis text size
                       theme.axis_y_text_size = 16,  # Changes y-axis text size
                       theme.legend_text_size = 8)   # Changes legend text size


```


<!--chapter:end:9901-FontChange.Rmd-->

# Change the Title/Subtitle/Caption


```{r How.2-Complete-Code-Example, fig.dim=c(13,12)}

survey1 %>%
  calculate_ind_smry("Q1COVID19",
                            "Algeria") %>%
  plot_ind_smry(.title = "New title",
                       .subtitle = "New subtitle",
                       .caption = "New caption")


```


<!--chapter:end:9902-TitleChange.Rmd-->


# Show Only Certain Countries? {#select-countries-chp}

Placeholder


## In Comparative Graphs
### Plots that go with `calculate_` functions {#select-countries-calculate}
### Plots with no `calculate_` functions {#select-countries-no-calculate}
## In Single Country Graphs

<!--chapter:end:9903-SelectCountries.Rmd-->


# Change the order of a stacked graph? {#order-change-stacked-graphs}

Placeholder


### Move One Factor {-}
### Swap Factors {-}

<!--chapter:end:9904-StackedOrder.Rmd-->


# Understand (some) Messages, Warnings, and Errors {#standard-warnings}

Placeholder


## Messages {#messages}
### Joining {#messages-join}
## Warnings
### `position_dodge()` {#warning-dodge}
### No Default Title/Subtitle {#warning-title}
#### Variable is Missing a Title/Subtitle {- #missing-title}
#### Multiquestion Graphs {- #multiquestion-titles}

<!--chapter:end:how-warnings.Rmd-->


# (PART) Appendix {-}
# Guide Features {-}

Placeholder



<!--chapter:end:Guide_Features.Rmd-->


# Installing and Updating `ArabBarometR` {-}

Placeholder


## Installing `ArabBaromtR` {-}
### Installing from GitHub {-}
### Downloading from GitHub {-}
## Updating `ArabBarometR` {-}
### Updating via `install_github` {-}
### Updating via downloads {-}

<!--chapter:end:install-update.Rmd-->


# A Note On Piping {#piping-note .unnumbered}

Placeholder


## Piping puts the object on the left into the function on the right. {-}
## Piping operators can chain code together. {-}
## The order matters. {-}

<!--chapter:end:piping_note.Rmd-->


# Using a `map()` {#using-map .unnumbered}

Placeholder


## Functions with One Argument {#map-basics -}
## Functions with Multiple Arguments {#advanced-map - }
## Conclusion {-}

<!--chapter:end:using-map.Rmd-->

